---
title: "Hypothesis Testing"
author: "Sravani Neelapala"
date: "2023-12-4"
output: html_document
---

```{r }
library(tidyverse)
library(dplyr)
```

```{r }
indata <- read.csv("/Users/eric/Global YouTube Statistics.csv")
dim(indata)
head(indata)
```

Reference : https://www.globalmediainsight.com/blog/youtube-users-statistics/

Calculating the mean of subscribers for the last 5 years.

# 1) Null Hypothesis and Alternate Hypothesis
Since the variance is unknown, we will perform single sample t-test H_O: = 38, H_1: < 38(one-sided test)

```{r }
# Reference distribution 
ggplot(data = indata) + 
geom_histogram(mapping = aes(x = log(subscribers), bins = 30))

subscribers <- ggplot(data = indata, aes(sample = log(subscribers)))
subscribers + stat_qq() + stat_qq_line()

#test statistic
t.test(log(indata$subscribers), alternative = c("less"), mu = log(38))

```

# Conclusion
** we fail to reject null hypothesis because that the subscribers represented in this sample **


# 2) Null hypothesis and Alternate Hypothesis

H_O : = variances are equal ; H_1 : = Variances are not equal(two-sided test).

```{r }
# Reference distribution

ggplot(data = indata) + geom_density(mapping = aes(x = log(uploads), color = as.factor(category)))

ggplot(data = indata) + geom_boxplot(mapping = aes(x = as.factor(category), y = log(uploads)))


data <- data.frame(
  category = c(" Autos & Vehicles", " Entertainment","Howto & Style", " nan","People & Blogs", " Shows", "  Travel & Events", "Comedy", " Film & Animation", " Movies", "News & Politics", " Pets & Animals", "Sports", "Education", "Gaming", "  Music", "Nonprofits & Activism", "Science & Technology", "Trailers" )
)
data$category <- as.factor(data$category)
str(data)

indata$category <- as.factor(indata$category)
summary(indata$category)

sum(is.na(indata$category))


# Test Statistic (F test)
Entertainment <- indata[which(indata$category == "Entertainment"), "uploads"]
Music <- indata[which(indata$category == "Music"), "uploads"]
var.test(log(Entertainment), log(Music))

```

# Conclusion
** we reject null hypothesis as p-value is less than the level of significance.**



