---
title: "EDA"
author: "Sravani Neelapala"
date: "09-06-2023"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r }
library(tidyverse)

```
```{r }
  df <- Orange
   dim(df)
   head(df, 35)
   summary(df) 
```
```  {r }
   Orange %>% 
     count(Tree) %>% 
     group_by(Tree) %>% 
     knitr :: kable(format = "html") 
   
```
```{r }
mode <- function(x,na.rm = TRUE){
  which.max(tabulate(x))
}
          
Orange %>%
  summarise(mean = mean(age, na.rm = TRUE), 
             median = median(age, na.rm = TRUE),
             mode = mode(age,na.rm = TRUE),
             var = var(age, na.rm = TRUE),
             sd = sd(age, na.rm = TRUE)) 
range(Orange$age)
 max(Orange$age) - min(Orange$age)

mode <- function(x, na.rm = TRUE){
  which.max(tabulate(x))
}

Orange %>%
  summarise(mean = mean(circumference, na.rm = TRUE), 
            median = median(circumference,na.rm = TRUE),
            mode = mode(circumference, na.rm = TRUE),
            var = var(circumference, na.rm = TRUE),
            sd = sd(circumference, na.rm = TRUE)) 
range(Orange$circumference)
 max(Orange$circumference) - min(Orange$circumference)

mode <- function(x,na.rm = TRUE){
  which.max(tabulate(x))
}

Orange %>%
  group_by(Tree) %>%
  summarise(mean = mean(circumference, na.rm = TRUE),
            median = median(circumference, na.rm = TRUE),
            mode = mode(circumference, na.rm = TRUE),
            var = var(circumference, na.rm = TRUE),
            sd = sd(circumference, na.rm = TRUE))

```

Orange data frame.
It has 35 observations and 3 variables.

There are two numeric variables "age" and "circumference". 

There is one categorical variable "Tree".

There are no missing values in Orange data set.

There are no duplicate rows.

Tree:
An ordered factor indicating the tree on which the measurement is made. The ordering is according to increasing maximum diameter.

Age:
A numeric vector giving the age of the tree (days since 1968/12/31)

Circumference:
A numeric vector of trunk circumferences (mm). This is probably “circumference at breast height”, a standard measurement in forestry.

There is a linear relation between age and circumference.As age increases the circumference of the tree also increases.

Levels of tree variable is 4<2<5<1<3.




```{r }
ggplot(data = Orange) +
   geom_histogram(mapping = aes(x = age), bins = 10) +
   labs(title = "HISTOGRAM OF AGE", x = "Age", y  = "Frequency") +
   theme(plot.title = element_text(color = "red", size = 25, face = "bold")) +
   theme(text = element_text(size = 20))
```

** The histogram graph shows a left-skewed distribution because most of the values in the 'age' variable lie between 400 and 1300. **


```{r }
ggplot(data = Orange) +
  geom_point(mapping = aes(x = age, y = circumference, color = factor(Tree), size = 20)) +
             labs(title = "SCATTERPLOT", x = "Age", y = "Circumference") + 
             theme(plot.title = element_text(color = "red", size = 25, face = "bold")) +
             theme(text = element_text(size = 20))
``` 

** From the scatterplot graph, we can observe that as age increases, circumference also increases, with colors assigned to the points based on the tree." **

```{r }
ggplot(data = Orange) + 
  geom_boxplot(mapping = aes(y = age, x = factor(Tree))) 
               
``` 

 ** The boxplot graph shows the distribution of ages of orange trees, categorized as 3 > 1 > 5 > 2 > 4.**
