---
title: "R Literate Programming"
author: "Sravani Neelapala"
date: "09-23-2023"
output: html_document
---

## R Markdown

```{r }
library(tidyverse)
```

```{r}
indata <- read.csv("/Users/eric/Desktop/rates/FertilityRates.csv")

# Check if data import was as expected
dim(indata)
head(indata)
```

** This data has 219 observations and 56 variables,but it seems like it is not yet in the tidy format. **

```{r }
# Is it a data frame or a tibble?
is.data.frame(indata)

```
** It checks whether the input data is a data frame or not. **

```{r }
indata <- as_tibble(indata)
is_tibble(indata)
```
** The 'indata' is in a data frame, and want to convert it into a tibble.**

```{r }
# Summary of data
summary(indata)
```
** Summary of the 'indata' dataset, including data for variables from 1960 to 2011, featuring the mean, median, and interquartile range (IQR). This summary will be helpful for graph plotting. **

```{r }
# Convert Country Name into a factor
indata$Country.Name <- as.factor(indata$Country.Name)

summary(indata$Country.Name)
```
** Converting the 'Country Name' variable into a  factor (categorical) variable and generating a summary of the variable. **

```{r }
# Convert Indicator Name into a factor
indata$Indicator.Name <- as.factor(indata$Indicator.Name)
summary(indata$Indicator.Name)
```
** Converting 'Indicator Name' into a factor(Categorical) variable and generating a  summary of the variable. **

```{r }
# Remove extra columns
indata_cleaned <- select(indata, -(Country.Code:Indicator.Code))

head(indata_cleaned)
```
** From 56 variables we are removing extra columns for better analysis **

```{r }
# Pivot to long dataset
indata_pivoted <- pivot_longer(indata_cleaned, c(str_c("X", c(1960:2011))), names_to = "Year", values_to="Fertility.Rates")

head(indata_pivoted)
```
** Changing the Columns(1960 - 2011) of the data frame into rows by using 'pivot_longer' function to check the fertility rates of countries.**

```{r }
# Format Year values
indata_pivoted$Year <- as.integer(str_sub(indata_pivoted$Year, 2,5))

# Check Missing Values
sum(is.na(indata_pivoted$Fertility.Rates))
```
** Taking substring from the string of the year. There are 1104 missing values in the data frame. **

```{r }
# Check missing values by country

## Step1: Filter by missing values
## setp 2: group by country
## Step3: Count number of values

indata_pivoted %>%  filter(is.na(Fertility.Rates)) %>% group_by(Country.Name) %>% summarise(count = n())
```
** It shows 27 countries have missing values and they are represented in rows by giving the count for each country missing values. **

```{r  }
# Fill missing values within countries

indata_filled <- indata_pivoted %>% group_by(Country.Name) %>% fill(Fertility.Rates, .direction ="downup") %>% ungroup()

## Check
indata_filled %>%  filter(is.na(Fertility.Rates)) %>% group_by(Country.Name) %>% summarise(count = n())

indata_filled <- indata_filled %>% filter(!is.na(Fertility.Rates))
```

** It shows that 9 countries have the same missing values, with a count of 52 for each. We are removing rows with more missing values for other countries. **

```{r }

ggplot(data = indata_filled) + geom_point(mapping = aes(x=Year, y = Fertility.Rates))
```


```{r }

# Plot Fertility Rates by Year
ggplot(data = indata_filled) + geom_point(mapping = aes(x=Year, y = Fertility.Rates), position = "jitter", alpha = 0.1) + geom_smooth(mapping = aes(x=Year, y = Fertility.Rates)) + labs(x = "Year", y = "Fertility Rates", title = "Fertility Rates over the years", subtitle = "Global fertility rates have decreased since 1960")
```

** Global fertility rates have been decreased from the year 1960 to 2011. **

```{r }

# Need a way to categorize 210 countries
## Option 1: subset the data

indata_subset <- filter(indata_filled, Country.Name %in% c("United States", "Mexico", "Canada"))


ggplot(data = indata_subset) + geom_line(mapping = aes(x=Year, y = Fertility.Rates, color = Country.Name), alpha = 0.5) + labs(x = "Year", y = "Fertility Rates", title = "Fertility Rates over the years", subtitle = "Global fertility rates have decreased since 1960")
```

** Global fertility rates has been decreasing for the countries United States, Mexico, and Canada since 1960. **

```{r }

## Option 2: Select based on statistics

# Top 10

indata_filled %>%  group_by(Country.Name) %>% summarise(avg = mean(Fertility.Rates)) %>% arrange(desc(avg)) %>% print(n = 10)
```

** Average for each country fertility rate. **

```{r }
# Bottom 10

indata_filled %>%  group_by(Country.Name) %>% summarise(avg = mean(Fertility.Rates)) %>% arrange(desc(avg)) %>% top_n(10) %>% ggplot() + geom_bar(mapping = aes(x = Country.Name, y = avg), stat = "identity") +coord_flip()
```

**  Bar graph displays a plot of the selected average fertility rates along with the country names.**

```{r }

### Option
library(countrycode)

indata_df <- as.data.frame(indata_filled)
indata_df$Continent.Name <- factor(countrycode(sourcevar = indata_df[,"Country.Name"], origin = "country.name", destination = "continent"))


indata_df$Region.Name <- factor(countrycode(sourcevar = indata_df[,"Country.Name"], origin = "country.name", destination = "region"))

head(indata_df)

indata <- as_tibble(indata_df)
```

** Adding the continent name and region name to check the fertility rate instead of country names for more analysis. **

```{r }

ggplot(data = indata) + geom_point(mapping = aes(x=Year, y = Fertility.Rates, color = Continent.Name), position = "jitter", alpha = 0.6) + labs(x = "Year", y = "Fertility Rates", title = "Fertility Rates over the years", subtitle = "Global fertility rates have decreased since 1960")
```

** A scatter plot shows how global fertility rates have decreased, based on continent names. ** 

```{r }
# Facet Plotting
ggplot(data =  indata) + geom_point(mapping = aes(x=Year, y = Fertility.Rates, color = Country.Name), position = "jitter", alpha = 0.2, show.legend = FALSE) + facet_wrap(~ Region.Name)
```

** Divided the countries into various regions and then created plots. **

```{r }

# Filtering and Potting
indata %>% filter(Region.Name == "Middle East & North Africa" & Continent.Name == "Asia") %>% ggplot() + geom_line(mapping = aes(x =Year, y = Fertility.Rates, color =  Country.Name), size = 1, linetype = 2)
```

** By considering the continent and region, we identified 14 countries. The plot reveals a bell-shaped trend from 1960 to 2000, followed by a decrease. **

```{r }

# Boxplot

ggplot(data =  indata, mapping = aes(x = Continent.Name, y = Fertility.Rates)) + geom_boxplot() + coord_flip()
```

** The African continent has the highest fertility rates, averaging around 7, while Asia exhibits a wide range of fertility rates, ranging from 2.6 to 6. **

```{r }

# Histogram
ggplot(data = indata) + geom_histogram(mapping = aes(x = Fertility.Rates), binwidth = 0.5)
```

** The histogram graph displays a right-skewed distribution, indicating that the average fertility rate tends to be higher, towards the right. **

```{r }

# Barchart

indata %>% group_by(Region.Name) %>% summarise(avg = mean(Fertility.Rates)) %>% ggplot(mapping = aes(x = reorder(Region.Name, -avg), y = avg, fill=Region.Name)) + geom_bar(stat = "identity") + coord_flip()

```

** Bar chart displaying the average fertility rate, grouped by region name after factorization. **
