---
title: "PCA"
author: "Sravani Neelapala"
date: "2023-11-25"
output: html_document
---
```{r }
library(tidyverse)
library(vcd)

```

```{r }
indata <- read.csv("/Users/eric/Global YouTube Statistics.csv")

# Check if data import was as expected
dim(indata)
head(indata)
```

** This data has 995 observations and 28 variables,but it seems like it is not yet in the tidy format.**

```{r }

#Is it a data frame?
is.data.frame(indata)
```

 ** It checks whether the input data is a data frame or not. **

```{r }
# data is in tibble format or not
indata <- as_tibble(indata)
is_tibble(indata)
```

** The 'indata' is in a data frame, and want to convert it into a tibble.**

```{r }
#Summary of data
summary(indata)
```

** Summary of the 'indata' dataset, comprising 28 variables of numerical, ordinal, continuous nature, featuring the mean, median, and interquartile range (IQR). This summary will be helpful for graph plotting. **

```{r }

# Convert Country into a factor 
indata$Country <- as.factor(indata$Country)

summary(indata$Country)

# Convert category into a factor 
indata$category <- as.factor(indata$category)

summary(indata$category)

#Convert created_year into a factor 
indata$created_year <- as.factor(indata$created_year)

summary(indata$created_year)

#Convert created_month into a factor 
indata$created_month <- as.factor(indata$created_month)

summary(indata$created_month)
```

** Converting the 6 variables from 28 into a factor(categorical) variable. **

```{r }
#Remove extra columns
indata_cleaned <- select(indata, -(Abbreviation:channel_type))

head(indata_cleaned)
```

** From 28 variables we are removing extra columns of Abbreviation,channel_type for better analysis **

```{r }
#checking for missing values
sum(is.na(indata))
```

** There are 1286 missing values in the data frame. **

```{r }
#checking for duplicate values
sum(duplicated(indata))
```

```{r }
# Import data
df <- indata
head(df)

# Include only numeric variables. We want to keep the name and make that as row names for the dataset
indata_ <- df[,-which(sapply(df, class) == "factor")]
head(indata_)

# Removing extra column
head(indata_)
indata_ <- indata_[, -c(1)]

indata_ <- indata_[, -which(names(indata_) == "video.views", " video_views_for_the_last_30_days", "Gross.tertiary.education.enrollment....", "Population", "Unemployment.rate"," Latitude", " Longitude")]
head(indata_)

cov_mat <- cov(indata_)
head(cov_mat)

```

```






